Opportunities for improvement in adult trauma patients admitted to the intensive care unit: A registry-based study

### 2024-03-11 manuscript.Rmd
11/3

There were 14,022 patients in the trauma registry between January 1 2014
and February 1 2023. 2679 of these patients were 
admitted to the ICU. 3 patients were then excluded as they were younger
than 15 years and 6 patients were excluded because they were dead on
arrival. 928 patients were excluded because there was no registration on whether there was an OFI or not. 293 patients were excluded because they had missing values in one or more variables.
This leaves us with 143 outcomes for OFI, and 1,306 outcomes for "No OFI".

@@

# Results
```{r}
library(gtsummary)
source("main.R")
```

@@

<!-- Flowchart -->

## Descriptive data

<!-- Sample characteristics - Table1, do I need to display number of missing for each variable? -->

## Main results

<!--  Adjusted and unadjusted analysis - Table 2 -->

>>>>

There were 14,022 patients in the trauma registry between January 1 2013
and February 28 2023. 2679 of these patients were 
admitted to the ICU. 3 patients were then excluded as they were younger
than 15 years and 6 patients were excluded because they were dead on
arrival. 928 patients were excluded because there was no registration on whether there was an OFI or not. 293 patients were excluded because they had missing values in one or more variables.
This leaves us with 143 outcomes for OFI, and 1,306 outcomes for "No OFI".

@@

# Results
## Participants
```{r, include=FALSE}
source("functions/flowchart.R")
```
```{r}
for (i in 1:(length(vert) - 1)) {
  connectGrob(vert[[i]], vert[[i + 1]], type = "vert") %>%
    print
}

connectGrob(vert$eligible, excluded, type = "L")
connectGrob(vert$included, excluded1, type = "L")

vert
excluded
excluded1
```

## Descriptive data
```{r include_scripts, echo=FALSE, include=FALSE}
source("functions/table1.R")
```
```{r}
table2
```

## Main results
```{r, include=FALSE}
source("functions/table2.R")
```
```{r}
table3_merge
```

@@
